---
title: "Report of Validation"
subtitle: "Conformity with standards and datacall"
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
header-includes:
  - \usepackage{fontawesome5}
  - \usepackage{xcolor}
  - \usepackage{colortbl}
  - \usepackage{booktabs}
  - \usepackage{float}
---
\definecolor{green1}{HTML}{008000}
\definecolor{orange1}{HTML}{FFA500}
\definecolor{red1}{HTML}{FF0000}

\begin{center}
\vspace{-0.5cm}
\noindent\rule{8cm}{0.4pt}

`r sprintf('Task: %s [%s] for %s',info$task_name,info$task_id,info$flagstate)`\\
`r config$dcf$context`\\
`r config$dcf$name`\\
`r info$date`\\

\noindent\rule{8cm}{0.4pt}
\end{center}

# Tested file information

* **Original File Name: **`r info$file`  
* **Original File Format: **`r info$format`  

# Validity of file
```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}

valid<-FALSE
if(ds_out$valid){
  valid <- TRUE
  if(is.null(gb_out)){
    valid<-FALSE
  }else{
    if(!gb_out$valid){
      valid<-FALSE
    }else{
      if(!is.null(dc_out)){
        if(!dc_out$valid){
          valid<-FALSE
        }else{
          valid<-TRUE
        }
      }
    }
  }
}

if(valid){
  cat("\\LARGE\\color{green1}\\faCheckCircle \\color{black} Data is valid")
}else{
  cat("\\LARGE\\color{red1}\\faTimesCircle \\color{black} Data is invalid")
}
```

# Validation summary
## Conformity with Standards - Data Structure

```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}

summary<-ds_out$summary
summary$test<-ifelse(summary$status=="EXISTING","E",ifelse(summary$type=="OPTIONAL","MO","MM"))
summary$icon<-ifelse(summary$test=="E","\\color{green1}\\faCheckCircle \\color{black}",
                     ifelse(summary$test=="MO","\\color{orange1}\\faExclamationTriangle \\color{black}",
                            "\\color{red1}\\faTimesCircle \\color{black}"))
summary$column<-gsub("_","\\_",summary$column,fixed=T)

summary<-summary[,c("column","type","status","icon")]

kableExtra::kable(summary,format = "latex",booktabs = T,escape=F,align = "llrc",col.names = NULL,linesep = "")%>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"),font_size = 8,full_width = F)%>%
  row_spec(which(summary$icon =="\\color{green1}\\faCheckCircle \\color{black}"), bold = T, color = "#008000", background = "#d3f4cc")%>%
  row_spec(which(summary$icon =="\\color{orange1}\\faExclamationTriangle \\color{black}"), bold = T, color = "#FFA500", background = "#f5dfc0")%>%
  row_spec(which(summary$icon =="\\color{red1}\\faTimesCircle \\color{black}"), bold = T, color = "#FF0000", background = "#ffbfc1")

```

## Conformity with Standards - Data Content

```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}

valid<-FALSE
if(!ds_out$valid){
  valid<-FALSE
}else{
  if(is.null(gb_out$valid)){
    valid<-FALSE
  }else{
    valid<-TRUE
  }
}

if(!valid){
  cat("\\normalsize Data content can't be tested because data strucure in not valid")
}else{
  summary<-gb_out$summary
  summary$icon<-ifelse(summary$status=="PASSED","\\color{green1}\\faCheckCircle \\color{black}",
                       ifelse(summary$status=="PASSED WITH WARNING","\\color{orange1}\\faExclamationTriangle \\color{black}",
                              "\\color{red1}\\faTimesCircle \\color{black}"))
  
  summary$column<-gsub("_","\\_",summary$column,fixed=T)
  
  kableExtra::kable(summary,format = "latex",booktabs = T,escape=F,align = "lrc",col.names = NULL,linesep = "")%>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"),font_size = 8,full_width = F)%>%
    row_spec(which(summary$status =="PASSED"), bold = T, color = "#008000", background = "#d3f4cc")%>%
    row_spec(which(summary$status =="WARNING"), bold = T, color = "#FFA500", background = "#f5dfc0")%>%
    row_spec(which(summary$status =="FAILED"), bold = T, color = "#FF0000", background = "#ffbfc1")
  
}

```


## Consistancy with Data Call

```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}

valid<-FALSE
if(!ds_out$valid){
  valid<-FALSE
  message<-"\\normalsize Data content can't be tested because data strucure in not valid"
}else{
  if(is.null(gb_out$valid)){
    valid<-FALSE
    message<-"\\normalsize Data content can't be tested because data strucure in not valid"
  }else{
    if(!gb_out$valid){
        valid<-FALSE
        message<-"\\normalsize Consistancy with data call can't be tested because data content in not valid"
    }else{
      if(is.null(dc_out$valid)){
        valid<-FALSE
        message<-"\\normalsize Consistancy with data call can't be tested because data content in not valid"
      }else{
        if(!dc_out$valid){
          valid<-FALSE
          message<-"\\normalsize Consistancy with data call can't be tested because no data call is open"
        }else{
          valid<-TRUE
        }
      }
    }
  }
}
if(!valid){
  cat(message)
}else{
  summary<-dc_out$summary
  summary$icon<-ifelse(summary$status=="PASSED","\\color{green1}\\faCheckCircle \\color{black}",
                       ifelse(summary$status=="PASSED WITH WARNING","\\color{orange1}\\faExclamationTriangle \\color{black}",
                              "\\color{red1}\\faTimesCircle \\color{black}"))
  
  summary$column<-gsub("_","\\_",summary$column,fixed=T)
  
  kableExtra::kable(summary,format = "latex",booktabs = T,escape=F,align = "lrc",col.names = NULL,linesep = "")%>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"),font_size = 8,full_width = F)%>%
    row_spec(which(summary$status =="PASSED"), bold = T, color = "#008000", background = "#d3f4cc")%>%
    row_spec(which(summary$status =="WARNING"), bold = T, color = "#FFA500", background = "#f5dfc0")%>%
    row_spec(which(summary$status =="FAILED"), bold = T, color = "#FF0000", background = "#ffbfc1")
  
}
```
