---
title: "Report of validation"
subtitle: "Conformity with data call"
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
header-includes:
  - \usepackage{fontawesome5}
  - \usepackage{xcolor}
  - \usepackage{colortbl}
  - \usepackage{booktabs}
  - \usepackage{float}
---
\definecolor{green1}{HTML}{008000}
\definecolor{orange1}{HTML}{FFA500}
\definecolor{red1}{HTML}{FF0000}
\definecolor{grey1}{HTML}{808080}

\begin{center}
\vspace{-0.5cm}
\noindent\rule{8cm}{0.4pt}

`r sprintf('Datacall-%s Task: %s [%s] for %s',submission$data_call_id,submission$task_name,submission$task_id,submission$reporting_entity)`\\
`r config$dcf$context`\\
`r config$dcf$name`\\
`r Sys.Date()`\\
\noindent\rule{8cm}{0.4pt}
\end{center}

# Validity of file
```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(out$valid){
  cat("\\LARGE\\color{green1}\\faCheckCircle \\color{black} Data is ready to be submitted")
}else{
  cat("\\LARGE\\color{red1}\\faTimesCircle \\color{black} Data is not consistent with the current data call")
}
```

# Summary of rules tested
```{r,results='asis', message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
          test<-out$tests
          test$icon<-ifelse(test$status=="PASSED","\\color{green1}\\faCheckCircle \\color{black}",
                            ifelse(test$status=="WARNING","\\color{orange1}\\faExclamationTriangle \\color{black}",
                                   ifelse(test$status=="FAILED","\\color{red1}\\faTimesCircle \\color{black}",
                                          "\\color{grey1}\\faBan \\color{black}")))
          
          kableExtra::kable(test,format = "latex",booktabs = T,escape=F,align = "lrl",col.names = NULL,linesep = "")%>%
          kableExtra::kable_styling(latex_options = c("HOLD_position"),font_size = 8,full_width = F)%>%
          row_spec(which(test$status =="PASSED"), bold = T, color = "#008000", background = "#d3f4cc")%>%
          row_spec(which(test$status =="WARNING"), bold = T, color = "#FFA500", background = "#f5dfc0")%>%
          row_spec(which(test$status =="FAILED"), bold = T, color = "#FF0000", background = "#ffbfc1")%>%
          row_spec(which(test$status =="NOT TESTED"), bold = T, color = "#808080", background = "#f0f0f0")  
```

# Details of errors
```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(nrow(out$errors)==0){
  cat("\\normalsize\\color{green1} No error detected \\color{black}")
}else{
  kableExtra::kable(out$errors,format = "latex", booktabs = T,linesep = "")%>%
    kableExtra::kable_styling(latex_options = c("striped","scale_down","HOLD_position"),font_size = 12,stripe_color="#e8e8e8")%>%
          row_spec(which(out$errors$type =="INFO"), bold = F, color = "black", background = "#fcfdd0")%>%
          row_spec(which(out$errors$type =="WARNING"), bold = F, color = "black", background = "#FDEBD0")%>%
          row_spec(which(out$errors$type =="ERROR"), bold = F, color = "black", background = "#F2D7D5")
}
```